A thesis draft

### 2018-09-10 draft.tex
Fix sentence

 In the modern mobile networking, these is a continuous necessity to 
improve the overall speed connection: important goals are low latency and a 
high throughtput. Mobile traffic is continuously surging every year, with 
the backbones having more data to process. In this context, in-hardware 
backbone solutions are becoming less efficent. Their time-to-deploy, in fact, is 
very high compared to the requirements of the network. With this trend, 
in-hardware solutions will not be able to keep up. Is with this considerations 
that software solutions are being proposed to become the new way to deploy 
network components. While less efficent, they are faster to bring them up. On 
top of that, new virtualization technologies such as Docker are becoming more 
and more mature to be employable for large-scale production environments, where 
new frameworks, called orchestrators, allow to easily manage the application 
lifecyle, i.e. deployment, scale up/down and finally, removal.

>>>>

 In the modern mobile networking, these is a continuous necessity to 
improve the overall speed connection: important goals are low latency and a 
high throughtput. Mobile traffic is continuously surging every year, with 
the backbones having more data to process. In this context, in-hardware 
backbone solutions are becoming less efficent. Their time-to-deploy, in fact, is 
very high compared to the requirements of the network. With this trend, 
in-hardware solutions will not be able to keep up. Is with this considerations 
that software solutions are being proposed to become the new way to deploy 
network components. While less efficent, they are faster to bring them up. On 
top of that, new virtualization technologies such as Docker are becoming more 
and more mature for being employed in large-scale production environments,
where new frameworks, called orchestrators (e.g. Kubernetes, Docker Swarm),
allow to easily manage the application lifecyle, i.e. deployment, scale up/down
and finally, removal.
